Fifteen years of decentralization attempts

### 2014-03-23 paper.tex
Improved the section on 'Tor stinks' and added a reference

		\subsection{The content on Tor}
			The anonymous communication with Tor can also be used for distribution illegal content or setting up illegal services. Illegal content and services such as drugs trading or child pornography, is a serious problem Tor is facing. A recent example is the shutdown of \emph{Silk Road}, an online market for trading drugs. This market operated as a hidden Tor service. These hidden services are accessed through their onion address and not through their IP-address, hiding the physical location of the service. This makes it very hard for agencies to track and shut down these operations.

			The illegal content travels unencrypted through a Tor exit node. Users running a Tor exit node, could be held responsible for distributing illegal content. A possible solution could be to filter the illegal content from the legal content. While content filtering is a viable solution, not many research has been done on it. It is also an open question whether filtering content is in line with the principles of Tor and the internet.

>>>>

		\subsection{Tor stinks}
			The anonymous communication with Tor can also be used for distribution illegal content or setting up illegal services. Illegal content and services is a serious problem Tor is facing. A recent example is the shutdown of \emph{Silk Road}, an online market for trading drugs. This market operated as a hidden Tor service. These hidden services are accessed through their onion address and not through their IP-address, hiding the physical location of the service. This makes it very hard for agencies to track and shut down these operations.

			A recent research on the content and popularity analysis of Tor hidden services \cite{biryukov2013content} has shown that although there are Tor hidden services that distributes illegal content, many hidden services are however resources devoted to human rights, freedom of speech and information which is prohibited in some countries. It is not clear which type of service is more popular on Tor.

			The illegal content travels unencrypted through a Tor exit node. Users running a Tor exit node, could be held responsible for distributing illegal content. The possibility of redirecting illegal content, refrains users from running an exit node. A possible solution could be to filter the illegal content from the legal content. While content filtering is a viable solution, it is an open question whether filtering content is in line with the principles of Tor and the internet. We think however that filtering the content on Tor, could make more users run an exit node and thus improve the quality of the network.
